Data Visualization

### 2018-11-24 papers/full_paper.Rmd
Add: Conditional expectations analysis

  options(stringsAsFactors=FALSE)
  options(xtable.comment = FALSE)
  options(xtable.caption.placement='top')
  #setwd('..')
  #source(file.path(getwd(), 'functions', 'abb_Functions.R'))
  source(file.path('c:/code', 'research', 'airbnbMelbourne', 'functions', 'abb_Functions.R'))

  # library(knitr)
  # knit_hooks$set(plot = function(x, options) {
  # paste('<figure><figcaption>', options$fig.cap, '</figcaption><img src="',
  #       opts_knit$get('base.url'), paste(x, collapse = '.'),
  #       '"></figure>',
  #       sep = '')})

@@

@@

The logistic regression models (Tables 3 and 4) highlight which characteristics lead to increased short term preference.  Small apartments in the central city are the best bet for generating greater revenues through short-term leasing.  More flexibility around the number of guests and the minimum stay increase the probability of short-term preference, while the reverse is true of cancellation policies (more strict equals higher short-term preference probability).  As a host, it appears to be best to do what you can to attract bookings and then make it difficult for those bookings to be cancelled.

@@

>>>>

  options(stringsAsFactors=FALSE)
  options(xtable.comment = FALSE)
  options(xtable.caption.placement='top')
  source(file.path('c:/code', 'research', 'airbnbMelbourne', 'functions', 'abb_Functions.R'))

@@

### Conditional Expecations

To better understand how the various factors impact the probability of short term preference we have estimated conditional expectations for a pair of exemplar homes -- a 1 bedroom, 1 bathroom and a 3 bedroom, 2 bathroom property.  The conditional probability expectations are generated by using Model 3 from Table 3 above to predict the short-term probability for most of the possible permutations of structure type, location, cancellation policy, guests per bedroom and minimum stay for the exemplar homes.  We plot these conditional probabilities in Figures 7 and 8.

![1 Bed, 1 Bath Conditional STP Probabilities](C:/Code/research/airbnbMelbourne/images/cpp_11.png)

For 1 bedroom 1 bathroom homes, investors looking for properties and strategies likely to lead to short-term preference should focus on factors in the upper left hand corner of Figure 7. Specifically, this means locations in the City-Core and City location and hosting policies that include strict cancellation policies.  Additionally, they should allow a high number of guests per bedrooms -- possibly by adding impromtu sleeping arrangements such as pull-out couches and sleeping dens.  Nearly all combination of the above locations, types and policies create at least a 50% probabilty of short-term preference.  Conversely, in the lower right hand corner of Figure 7 we see factor combination of which none create a short-term probability of 50% or greater.  In short, suburban locations and any properties managed with flexible cancellation policies, long minimum stays and few guests per bedroom are better off in the long-term market.

![3 Bed, 2 Bath Conditional STP Probabilities](C:/Code/research/airbnbMelbourne/images/cpp_32.png)

Overall, the trends for 3 bedroom, 2 bathroom homes (Figure 8) are similar to those of 1 bedroom, 1 bathroom homes, though with slighly lower probabilities of STP across all factor permutations.  Again, apartments in the City-Core and City offer good short-term rental opportunties if managed properly (short term stay minimums and reasonably high number of guests allowed).

@@

The logistic regression models (Tables 3 and 4) and the conditional expectation plots (Figures 7 and 8) highlight which characteristics lead to increased short term preference.  Small apartments in the central city are the best bet for generating greater revenues through short-term leasing.  More flexibility around the number of guests and the minimum stay increase the probability of short-term preference, while the reverse is true of cancellation policies (more strict equals higher short-term preference probability). In short, investors should look for apartment units in central city locations and then,  as a host, aggressively attract bookings and then make it difficult for those bookings to be cancelled.

@@

The cancellation policy variable carries a stronger signal than might be expected.  We suspect that some of this signal may be a result of strict cancellation policies being a luxury that only the best -- both in terms of the property as well as the management -- short-term rentals can get away with.  As such, this variable may be serving as a proxy for one or more unobserved variables and, we believe, warrants more attention in future work.

### 2018-11-24 papers/round_3_reviews.Rmd
Add: Conditional expectations analysis

---
title: "To Airbnb?: Factors impacting short-term leasing preference"
subtitle: 'Reviewer Responses'
date: "11/8/2018"
output:
  pdf_document: default
  html_document: default
header-includes: 
   - \usepackage{setspace}\doublespacing
   - \usepackage{caption}
   - \captionsetup[table]{skip=10pt}
geometry: margin=3.3cm
bibliography: abb.bib
---

@@

1. Bolstered the literature review
* Provided larger coverage of the short-term rental issues by extending discussion to some non-Real Estate centric work [@kakar2018visible; @cheng2018sharing]
* Added in a few very recent publications to help solidify the importance of this work [@manning2018hotel] and to provide deeper look at previous short term rental pricing work[@gibbs2018use; @gibbs2018pricing; @oskam2018s]

>>>>

---
title: "To Airbnb?: Factors impacting short-term leasing preference"
subtitle: 'Review Update'
date: "11/22/2018"
output:
  pdf_document: default
  html_document: default
header-includes: 
   - \usepackage{setspace}\doublespacing
   - \usepackage{caption}
   - \captionsetup[table]{skip=10pt}
geometry: margin=3.3cm
bibliography: abb.bib
---

@@

#### 1. Bolstered the literature review

* Provides larger coverage of the short-term rental issues by extending discussion to some non-Real Estate centric work [@kakar2018visible; @cheng2018sharing]

* Adds in a few very recent publications to help solidify the importance of this work [@manning2018hotel] and to provide deeper look at previous short term rental pricing work[@gibbs2018use; @gibbs2018pricing; @oskam2018s]

&nbsp; 
&nbsp;

#### 2. Added Conditional Expectations Section

* Provides a clearer look at how the various factor influence short-term preference

* Provides more explicit advise on which situations and strategies are most promising for investors looking for short-term preferable properties.

&nbsp; 
&nbsp;

### 2018-11-24 scripts/4_data_analysis.Rmd
Add: Conditional expectations analysis

@@

  dir.create(file.path(getwd(), 'data', 'analyzed'))
  save(str_tdf, ltr_tdf, ltr_df, col_df, suburb_sf, studyarea_sf, sa1_sf, str_sf, ltr_sf,
       pot_glms, core_suburbs, str_tdf_all, pot_mc_glms, pot_us_glms,
       #pot_ht_glms, lik_ht_glms,
       file=file.path(getwd(), 'data', 'analyzed', 'analyzed_data.RData'))

>>>>

### Prediction Chart

```{r}

# Create New variables

 str_tdf$gpb <- str_tdf$max_guests / str_tdf$bedrooms
 str_tdf$canc <- ifelse(str_tdf$canc_policy == 'Flexible', 1, 0)

# Recreate Model

 pred_model <- glm(pot_pref ~ type + as.factor(bedbath) + as.factor(geo_mrkt) +
                    gpb + min_stay + canc,
                      family=binomial(link='logit'),
                      data=str_tdf)

```{r}

### Create variables for pred

  bedbath <- unique(str_tdf$bedbath)
  type <- unique(str_tdf$type)
  geo_mrkt <- unique(str_tdf$geo_mrkt)
  canc <- c(0,1)
  min_stay <- c(1,2,3,4,7)
  gpb <- 1:5

  pred_df <- expand.grid(bedbath, type, geo_mrkt, canc, min_stay, gpb)
  names(pred_df) <- c('bedbath', 'type', 'geo_mrkt', 'canc', 'min_stay', 'gpb')

  pred_df$id <- apply(pred_df, 1, function(x) paste0(substr(x['type'], 1,1),
                                                     x['bedbath'], 
                                                     substr(x['geo_mrkt'], 1, 5)))

  str_tdf$id <- apply(str_tdf, 1, function(x) paste0(substr(x['type'], 1,1),
                                                     x['bedbath'], 
                                                     substr(x['geo_mrkt'], 1, 5)))
  pred_df$aid <- apply(pred_df, 1, function(x) paste0(x['bedbath'], 
                                                      substr(x['geo_mrkt'], 1, 5)))
  str_tdf$aid <- apply(str_tdf, 1, function(x) paste0(x['bedbath'], 
                                                      substr(x['geo_mrkt'], 1, 5)))

```{r}

# Make predictions
  pred_df$raw <- predict(pred_model, newdata = pred_df)
  pred_df$prob <-  exp(pred_df$raw)/(1+exp(pred_df$raw))
  pred_df$sh <- ifelse(pred_df$prob > .5, 1, 0)
  pred_df$sh <- factor(pred_df$sh, levels = c(1,0))

  #pred_df$min_stay <- as.factor(pred_df$min_stay)
  pred_df$gpb <- as.factor(pred_df$gpb)
  pred_df$cc <- ifelse(pred_df$canc == 1, 'Flexible', 'Strict')
  pred_df$ct <- paste0(ifelse(pred_df$type == 'House', 'House', 'Apt'), 
                       " - ",  pred_df$cc)

  pred_df$ms <- as.character(pred_df$min_stay)
  pred_df$ms[pred_df$ms == '4'] <- '4-6'
  pred_df$ms[pred_df$ms == '7'] <- '7+'
  pred_df$ms <- factor(pred_df$ms, levels=c('1', '2', '3', '4-6', '7+'))

  pred_df$sm <- as.character(pred_df$geo_mrkt)
  pred_df$sm[pred_df$sm == 'city-core'] <- 'City-Core'
  pred_df$sm[pred_df$sm == 'city'] <- 'City'
  pred_df$sm[pred_df$sm == 'beach'] <- 'Beach'
  pred_df$sm[pred_df$sm == 'suburban'] <- 'Suburban'
  pred_df$sm <- factor(pred_df$sm, levels = c('City-Core', 'City', 'Beach', 'Suburban'))

  pred_df$ct <- factor(pred_df$ct, levels = c('Apt - Strict', 'House - Strict', 
                                              'Apt - Flexible', 'House - Flexible'))

@@

  dir.create(file.path(getwd(), 'data', 'analyzed'))
  save(str_tdf, ltr_tdf, ltr_df, col_df, suburb_sf, studyarea_sf, sa1_sf, str_sf, ltr_sf,
       pot_glms, core_suburbs, str_tdf_all, pot_mc_glms, pot_us_glms,
       #pot_ht_glms, lik_ht_glms, pred_df, 
       file=file.path(getwd(), 'data', 'analyzed', 'analyzed_data.RData'))

### 2018-11-24 scripts/5_data_viz.Rmd
Add: Conditional expectations analysis

>>>>

```{r}
 ## 1/1 plots
  x <- pred_df[pred_df$bedbath == "1_1", ]
  cap11 <- paste0('Plot shows the conditional probability of short term preference for ',
                  '1 bedroom, 1 bathroom homes given differences\n',
                  'in their structure type (Apt vs House), cancellation policy (strict',
                  ' vs flexible), location (City-Core, City, Beach, Suburban),\n',
                  'Number of allowed guest per bedroom and minimum number of night stay ',
                  'reguired. Larger and darker dots indicate\na higher probabilty ',
                  'of short-term preference with full dots showing 50%+.')

  ggplot(x, aes(x=ms, y=gpb, color = prob)) + 
    geom_point(aes(shape = sh, size = prob)) + 
    facet_grid(sm~ct) +
    scale_color_gradient(low='gray80', high='black', name='STP Probability',
                         labels = c('0%', '25%', '50%', '75%'),
                         breaks = c(0,.25, .50, .75)) +
    scale_shape_manual(values = c(16,1), name = 'Is STP?', labels=c('True', 'False')) + 
    scale_size(range = c(.5, 3), guide = FALSE) + 
    xlab('\n Minimum Stay  (In Days)\n') +
    ylab('Allowed Guests per Bedroom\n') + 
    labs(title = '1 Bed, 1 Bath Home - Conditional STP Probabilities\n',
         caption = cap11) + 
    theme(plot.caption=element_text(hjust = 0),
          plot.title = element_text(hjust = 0.5)) -> cpp_11

  png(filename = file.path(getwd(), 'images', "cpp_11.png"), 
       width = 7, height = 5, units = 'in', res = 300)
     cpp_11
  dev.off()

```{r}

 ## 1/1 plots
  x <- pred_df[pred_df$bedbath == "3_2", ]
  cap11 <- paste0('Plot shows the conditional probability of short term preference for ',
                  '3 bedroom, 2 bathroom homes given differences\n',
                  'in their structure type (Apt vs House), cancellation policy (strict',
                  ' vs flexible), location (City-Core, City, Beach, Suburban),\n',
                  'Number of allowed guest per bedroom and minimum number of night stay ',
                  'reguired. Larger and darker dots indicate\na higher probabilty ',
                  'of short-term preference with full dots showing 50%+.')

  ggplot(x, aes(x=ms, y=gpb, color = prob)) + 
    geom_point(aes(shape = sh, size = prob)) + 
    facet_grid(sm~ct) +
    scale_color_gradient(low='gray80', high='black', name='STP Probability',
                         labels = c('0%', '25%', '50%', '75%'),
                         breaks = c(0,.25, .50, .75)) +
    scale_shape_manual(values = c(16,1), name = 'Is STP?', labels=c('True', 'False')) + 
    scale_size(range = c(.5, 3), guide = FALSE) + 
    xlab('\n Minimum Stay (In Days)\n') +
    ylab('Allowed Guests per Bedroom\n') + 
    labs(title = '3 Bed, 2 Bath Home - Conditional STP Probabilities\n',
         caption = cap11) + 
    theme(plot.caption=element_text(hjust = 0),
          plot.title = element_text(hjust = 0.5)) -> cpp_32

  png(filename = file.path(getwd(), 'images', "cpp_32.png"), 
       width = 7, height = 5, units = 'in', res = 300)
     cpp_32
  dev.off()
